Constant-sized correlations are sufficient for robust self-testing of maximally entangled states with unbounded dimension

### 2019-05-06 Draft/draft.tex
Some changes to section 1 and 6 -- Honghao

In order to accomplish our goal, we introduce new techniques for robust self-testing.
We use a different variant of the weighted CHSH inequality, \hf{which was first introduced in Ref.~\cite{acin2012}
for studying randomness and entanglement and not used in the self-testing literature before}, 
to enforce the eigenvalue of the product of two binary observables used in the weighted CHSH test.
The idea of decompose the unitaries of arbitrary order into binary observables was first introduced by Slofstra \cite{slofstra2017}.
We use a different way to decompose the unitaries, which can be seen as the inverse of Jordan's lemma, and
apply it to self-testing proofs.
Comparing to the previous approaches, which aim to enforcing eigenvalues of individual operators, our approach
gives us more flexibility in designing the correlation and easier generalization of our proof techniques. 
The other contribution is that we prove self-testing without using the anti-commutation relation between Pauli operators,
or the generalized version of it, 
which is the core idea in \hf{most of} the previous self-testing results.
\carl{Are we sure about that ("all")?}
Instead, we find a new relation that should be enforced.

pair of operators that can generate the ring of matrices over complex numbers.
\carl{Our work is heavily based on \cite{slofstra2017}, and we need to make that clearer.}
\hfc{How about now?}

@@

		&\ket{\psi_2} = 1/2(M_{\nr+1}^1 + iM_{\nr+2}M_{\nr+1}^0 -iM_{\nr+2}M_{\nr+1}^1 + M_{\nr+1}^0)  \ket{\psi} \\
		&\ket{\psi_3} =1/2 (N_{\nr+1}^0 - iN_{\nr+2}N_{\nr+1}^1+iN_{\nr+2}N_{\nr+1}^0 + N_{\nr+1}^1)\ket{\psi}\\
		&\ket{\psi_4} =1/2(N_{\nr+1}^1 + iN_{\nr+2}N_{\nr+1}^1 -iN_{\nr+2}N_{\nr+1}^0 + N_{\nr+1}^1)\ket{\psi}

@@

	 \label{eq:psi1_eq} &\ket{\psi_1} \appd{O(\sd \sr\qe)} \ket{\psi_3} \text{ and } \ket{\psi_2} \appd{O(\sd \sr\qe)} \ket{\psi_4}, \\
	 \label{eq:psi1_sum} &M_\ast^\diamond \ket{\psi} \appd{O( r\se)} \ket{\psi_1}+\ket{\psi_2}, \\
	 \label{eq:psi1_orth} &\braket{\psi_2}{\psi_1} \appd{O( r\se)} 0,\\
	 \label{eq:psi1_norm} &\norm{\ket{\psi_i}}^2 \appd{O(r\se)} 1/(d-1) \quad \text{ for } i = 1, 2, 3, 4,\\

@@

	\textbf{To prove \cref{eq:psi1_sum}}, we use the definition of $\ket{\psi_1}$ and $\ket{\psi_2}$ and get 
	\begin{align*}
		\ket{\psi_2} + \ket{\psi_1} = 1/2( 2M_{\nr+1}^0 + 2M_{\nr+1}^1) \ket{\psi} \appd{O(r\se)} M_\ast^\diamond \ket{\psi}.
	\end{align*}

	\textbf{To prove \cref{eq:psi1_orth}}, we expand the inner product and get 
	\begin{align*}
		&\braket{\psi_1}{\psi_2}\\
	 = &1/4\bra{\psi}(M_{\nr+1}^0 - iM_{\nr+1}^1M_{\nr+2} + iM_{\nr+1}^0M_{\nr+2} +M_{\nr+1}^1)\\
	 &(M_{\nr+1}^1 + iM_{\nr+2}M_{\nr+1}^0 -iM_{\nr+2}M_{\nr+1}^1 + M_{\nr+1}^0)\ket{\psi}\\
	 =& 1/2i \bra{\psi}(M_{\nr+1}^0M_{\nr+2}M_{\nr+1}^0-M_{\nr+1}^1M_{\nr+2}M_{\nr+1}^1\ket{\psi}.
	\end{align*}
	Then we will show that $\bra{\psi} M_{\nr+1}^0M_{\nr+2}M_{\nr+1}^0 \ket{\psi} \appd{O( r\se)} 0$ as follows
	\begin{align*}
	 \bra{\psi}(M_{\nr+1}^0M_{\nr+2}M_{\nr+1}^0\ket{\psi} &\appd{O(r\se)}  \bra{\psi}(N_{\nr+1}^0M_{\nr+2}N_{\nr+1}^0)\ket{\psi}\\
	  &=\bra{\psi}M_{\nr+2}N_{\nr+1}^0)\ket{\psi}\\
	&\appd{O(r^2\ep)} 0,
	\end{align*}
	where the last approximation comes from the correlation.
	Similarly, we have 
	\begin{align*}
	\bra{\psi}(M_{\nr+1}^1M_{\nr+2}M_{\nr+1}^1\ket{\psi} \appd{O(r\se)} \bra{\psi} M_{\nr+2}N_{\nr+1}^1 \ket{\psi} \appd{O(r^2\ep)} 0.
	\end{align*}
	Hence, $\braket{\psi_2}{\psi_1} \appd{O(r\se)} 0$.

@@

	\textbf{To prove \cref{eq:psi1_eig2}},
	we first show that $M_1M_2 \ket{\psi_3}\appd{O(\sr \qe/\sd)} \omega_d^{-1} \ket{\psi_3}$, then we 
	use the fact that $\ket{\psi_3} \appd{O(\sd \sr\qe)} \ket{\psi_1}$ to draw the conclusion.

@@

		M_1M_2 \ket{\psi_3} \appd{O(\sr \qe/\sd)} \omega_d^{-1}\ket{\psi_3},

@@

	where we use the fact that $\ket{\psi_3} = 1/2(\1+iN_{\nr+2})(N_{\nr+1}^0 - i N_{\nr+2}N_{\nr+1}^1) \ket{\psi}$
	In the end, the relation $\ket{\psi_1}  \appd{O(\sd \sr\qe)} \ket{\psi_3}$ gives us that 

>>>>

In order to accomplish our goal, we first design a linear system game to enforce the 
relation $UOU\ct = O^r$, with the inspiration comes from Slofstra \cite{slofstra2017}.
Unlike previous self-testing proofs, which tries to enforce the anti-commutation relation
between Pauli operators of dimension $2$, $XZ=-ZX$, or the generalized anti-commutation relation 
between Pauli operators of higher dimension, $XZ = \omega_d ZX$, the dimension $d$ is implicit in our
relation. 
The implication is that the eigenvalues of $O$ are powers of $\omega_d$, for
some $d$ whose primitive root is $r$, and $U$ only permutes the eigenvectors of $O$. 
Since winning the linear system game requires that Alice
and Bob share a state $\ket{\psi}$, which satisfies the condition that 
$O_A \x O_B \ket{\psi} = \ket{\psi}$, intuitively, we know that 
$\ket{\psi}$ is spanned by eigenvectors of $O$. 
The other specialty of the linear system game is that it forces Alice and Bob to have binary observables
whose products are the speical unitaries $U$ and $O$, because the answers to the questions of the 
linear system games are binary. 
The idea of decompose the unitaries of arbitrary order into binary observables was also first introduced by Slofstra \cite{slofstra2017}.
We use a different way to decompose the unitaries, which can be seen as the inverse of Jordan's lemma, 
The fact that Alice and Bob only have binary observables make it easier for us 
to compose the linear system game with another test, which we call the extended weighted CHSH test.
The core idea of the extended weighted CHSH test is to certify that Alice and Bob's observables and state 
for the linear system game can also be used to violate the weighted CHSH inequality \cite{acin2012} maximally.
We find that the maximal violation of the weighted CHSH inequality can certify the eigenvalues of the product
of Bob's observables. 
At this point, we can use the extended weighted CHSH test to certify that
$O$ has eigenvalue $\omega_d$ and $d$ is prime, then we know $O$ also has eigenvalues $\omega_d^j$ for $j = 1 \dots d-1$.
In the end, we can use the generalized swap isometry \cite{yang2013} to prove our robust self-testing.
Note that our robust self-testing proof follows a different line of arguments from what was originally
proposed in Ref.~\cite{yang2013}.
\carl{Our work is heavily based on \cite{slofstra2017}, and we need to make that clearer.}
\hfc{How about now?}

@@

		%&\ket{\psi_2} = 1/2(M_{\nr+1}^1 + iM_{\nr+2}M_{\nr+1}^0 -iM_{\nr+2}M_{\nr+1}^1 + M_{\nr+1}^0)  \ket{\psi} \\
		&\ket{\psi_2} =1/2 (N_{\nr+1}^0 - iN_{\nr+2}N_{\nr+1}^1+iN_{\nr+2}N_{\nr+1}^0 + N_{\nr+1}^1)\ket{\psi}\\
		%&\ket{\psi_4} =1/2(N_{\nr+1}^1 + iN_{\nr+2}N_{\nr+1}^1 -iN_{\nr+2}N_{\nr+1}^0 + N_{\nr+1}^1)\ket{\psi}

@@

	 \label{eq:psi1_eq} &\ket{\psi_1} \appd{O(\sd \sr\qe)} \ket{\psi_2},\\ 
	 %\text{ and } \ket{\psi_2} \appd{O(\sd \sr\qe)} \ket{\psi_4}, \\
	 %\label{eq:psi1_sum} &M_\ast^\diamond \ket{\psi} \appd{O( r\se)} \ket{\psi_1}+\ket{\psi_2}, \\
	 %\label{eq:psi1_orth} &\braket{\psi_2}{\psi_1} \appd{O( r\se)} 0,\\
	 \label{eq:psi1_norm} &\norm{\ket{\psi_i}}^2 \appd{O(r\se)} 1/(d-1) \quad \text{ for } i = 1, 2\\

@@

@@

	\textbf{To prove \cref{eq:psi1_eig2}},
	we first show that $M_1M_2 \ket{\psi_2}\appd{O(\sr \qe/\sd)} \omega_d^{-1} \ket{\psi_2}$, then we 
	use the fact that $\ket{\psi_2} \appd{O(\sd \sr\qe)} \ket{\psi_1}$ to draw the conclusion.

@@

		M_1M_2 \ket{\psi_2} \appd{O(\sr \qe/\sd)} \omega_d^{-1}\ket{\psi_2},

@@

	where we use the fact that $\ket{\psi_2} = 1/2(\1+iN_{\nr+2})(N_{\nr+1}^0 - i N_{\nr+2}N_{\nr+1}^1) \ket{\psi}$
	In the end, the relation $\ket{\psi_1}  \appd{O(\sd \sr\qe)} \ket{\psi_2}$ gives us that 
